WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-06-10 results/sec_2-workload.tex
Done scan reading
Remove And start

\begin{minipage}{\linewidth}
\begin{lstlisting}[language=sh, caption=Preparation of precipitation data.]
Set ROOT_DIR=~/wdias/wdias-performance-test
-h | --help: Usage
  setup_precipitation.sh  <COMMAND>
    - COMMAND: help | extract | prepare | cleanup | populate
  e.g.
  setup_precipitation.sh prepare
    Segregate single file data into multiple files based on date. And Separate into main directories of 15min, 30min, 60min and create tar files
  setup_precipitation.sh extract
    Extract the tar files into 15min, 30min and 60min
  setup_precipitation.sh cleanup
    Clean up extracted directories
\end{lstlisting}
\end{minipage}

@@

\begin{minipage}{\linewidth}
\begin{lstlisting}[language=sh, caption= Preparation of water-level data.]
Set ROOT_DIR=~/wdias/wdias-performance-test
-h | --help: Usage
  setup_water-level.sh  <COMMAND>
    - COMMAND: help | extract | prepare | cleanup | populate
  e.g.
  setup_water-level.sh prepare
    Segregate single file data into multiple grid file directories based on date. And Separate into main directories of 15min, 30min, 60min and create tar files
  setup_water-level.sh extract
    Extract the tar files into 15min, 30min and 60min
  setup_water-level.sh cleanup
    Clean up extracted directories
\end{lstlisting}
\end{minipage}

@@

\begin{itemize}
    \item HTTP request defaults
    \item HTTP header manager
    \item Timeseries metadata CSV
    \item If scalar or vector
        \begin{itemize}
            \item Insert timeseries
        \end{itemize}
    \item If a grid
    \begin{itemize}
        \item Insert grid timeseries
    \end{itemize}
    \item Wait for extensions timeseries
    \item Interest area preprocessor
    \item Query if scalar or vector
    \item Retrieve if scalar or vector
        \begin{itemize}
            \item Retrieve timeseries
        \end{itemize}
    \item Retrieve if a grid
    \begin{itemize}
        \item Retrieve grid timeseries
    \end{itemize}
    \item Increment date
    \item Throughput shaping timer prod
\end{itemize}

@@

\begin{itemize}
    \item HTTP request defaults
    \item HTTP header manager
    \item Locations CSV
    \item Interest area preprocessor
    \begin{itemize}
        \item /Location: * → Locations
    	\item /Location: Area → Locations
    	\item /Parameter: Location → Parameters
    	\item /Parameter: Locations → Parameters
    	\item /Timeseries: Location → Timeseries
    	\item /Timeseries: Locations → Timeseries
    	\item /Timeseries: Locations, Parameter → Timeseries
    	\item /Timeseries: Area → Timeseries
    	\item /Timeseries: Area, Parameter → Timeseries
    	\item /Timeseries: *, Parameter → Timeseries
    	\item /Timeseries: * → Timeseries
	\end{itemize}
\end{itemize}

>>>>

\begin{minipage}{\linewidth}
\begin{lstlisting}[language=sh, caption=Preparation of precipitation data.]
Set ROOT_DIR=~/wdias/wdias-performance-test
-h | --help: Usage
  setup_precipitation.sh  <COMMAND>
    - COMMAND: help | extract | prepare | cleanup | populate
  e.g.
  setup_precipitation.sh prepare
    Segregate single file data into multiple files based on date. And separate into main directories of 15min, 30min, 60min and create tar files
  setup_precipitation.sh extract
    Extract the tar files into 15min, 30min and 60min
  setup_precipitation.sh cleanup
    Clean up extracted directories
\end{lstlisting}
\end{minipage}

@@

\begin{minipage}{\linewidth}
\begin{lstlisting}[language=sh, caption= Preparation of water-level data.]
Set ROOT_DIR=~/wdias/wdias-performance-test
-h | --help: Usage
  setup_water-level.sh  <COMMAND>
    - COMMAND: help | extract | prepare | cleanup | populate
  e.g.
  setup_water-level.sh prepare
    Segregate single file data into multiple grid file directories based on date. And separate into main directories of 15min, 30min, 60min and create tar files
  setup_water-level.sh extract
    Extract the tar files into 15min, 30min and 60min
  setup_water-level.sh cleanup
    Clean up extracted directories
\end{lstlisting}
\end{minipage}

@@

\begin{itemize}
    \item HTTP request defaults
    \item HTTP header manager
    \item Timeseries metadata CSV
    \item If scalar or vector then insert timeseries, otherwise insert grid timeseries
    \item Wait for extensions timeseries
    \item Interest area preprocessor
    \item Query if scalar or vector
    \item If scalar or vector then retrieve timeseries, otherwise retrieve grid timeseries
    \item Increment date
    \item Throughput shaping timer prod
\end{itemize}

@@

\begin{itemize}
    \item HTTP request defaults
    \item HTTP header manager
    \item Locations CSV
    \item Interest area preprocessor
    \begin{itemize}
        \item /Location: * $\rightarrow$ Locations
    	\item /Location: Area $\rightarrow$ Locations
    	\item /Parameter: Location $\rightarrow$ Parameters
    	\item /Parameter: Locations $\rightarrow$ Parameters
    	\item /Timeseries: Location $\rightarrow$ Timeseries
    	\item /Timeseries: Locations $\rightarrow$ Timeseries
    	\item /Timeseries: Locations, Parameter $\rightarrow$ Timeseries
    	\item /Timeseries: Area $\rightarrow$ Timeseries
    	\item /Timeseries: Area, Parameter $\rightarrow$ Timeseries
    	\item /Timeseries: *, Parameter $\rightarrow$ Timeseries
    	\item /Timeseries: * $\rightarrow$ Timeseries
	\end{itemize}
\end{itemize}
